---
title: "Gene Level Homology"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{bash, eval = F}
# blast/2.12.0+
blastp \
 -db ../Sequences/${Seq_1} \
 -query ../Sequences/${Seq_2} \
 -max_target_seqs 5 \
 -out ${Name_1}_vs_${Name_2}.out \
 -evalue 1e-5 \
 -num_threads 4 \
 -outfmt "6 std qlen slen"

blastp \
 -db ../Sequences/${Seq_2} \
 -query ../Sequences/${Seq_1} \
 -max_target_seqs 5 \
 -out ${Name_2}_vs_${Name_1}.out \
 -evalue 1e-5 \
 -num_threads 4 \
 -outfmt "6 std qlen slen"
```

### Comparing the ancestral B.rapa and B.oleracea to DaAe

```{r}
library(tidyverse)
headers <- c("query.acc.ver","subject.acc.ver","pct.identity","alignment.length","mismatches","gap.opens","q.start","q.end","s.start","s.end","evalue","bit.score","query.length","subject.length")
```
## DaAE
```{r}
# Finding the RBH between each genome/subgenome
# Find the RBH between B.rapa and B.oleracea
Brapa_vs_Boleracea <- read_table("BlastP/Brapa_Z1_V2_vs_Boleracea_HDEM.out.gz", col_names = headers)
Boleracea_vs_Brapa <- read_table("BlastP/Boleracea_HDEM_vs_Brapa_Z1_V2.out.gz", col_names = headers)

# Filter for best hits
Brapa_vs_Boleracea <- Brapa_vs_Boleracea %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
Boleracea_vs_Brapa <- Boleracea_vs_Brapa %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Brapa_and_Boleracea <- inner_join(Brapa_vs_Boleracea,
                                  Boleracea_vs_Brapa,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for DaAe_A and Brapa
# Find the RBH between DaAe_A and Brapa
Brapa_vs_DaAe <- read_table("BlastP/Brapa_Z1_V2_vs_DaAe.out.gz", col_names = headers) %>% filter(!grepl("_Random_", query.acc.ver))
Brapa_vs_DaAe_A <- Brapa_vs_DaAe %>%
  filter(grepl("BnachrA",query.acc.ver))
DaAe_vs_Brapa <- read_table("BlastP/DaAe_vs_Brapa_Z1_V2.out.gz", col_names = headers) %>% filter(!grepl("_Random_", subject.acc.ver))
DaAe_A_vs_Brapa <- DaAe_vs_Brapa %>%
  filter(grepl("BnachrA",subject.acc.ver))

# Filter for best hits
Brapa_vs_DaAe_A <- Brapa_vs_DaAe_A %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
DaAe_A_vs_Brapa <- DaAe_A_vs_Brapa %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Brapa_and_DaAe_A <- inner_join(Brapa_vs_DaAe_A,
                                  DaAe_A_vs_Brapa,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for DaAe_C and Brapa
# Find the RBH between DaAe_C and Brapa
Brapa_vs_DaAe_C <- Brapa_vs_DaAe %>%
  filter(grepl("BnachrC",query.acc.ver))
DaAe_C_vs_Brapa <- DaAe_vs_Brapa %>%
  filter(grepl("BnachrC",subject.acc.ver))

# Filter for best hits
Brapa_vs_DaAe_C <- Brapa_vs_DaAe_C %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
DaAe_C_vs_Brapa <- DaAe_C_vs_Brapa %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Brapa_and_DaAe_C <- inner_join(Brapa_vs_DaAe_C,
                                  DaAe_C_vs_Brapa,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for DaAe_A and Boleracea
# Find the RBH between DaAe_A and Boleracea
Boleracea_vs_DaAe <- read_table("BlastP/Boleracea_HDEM_vs_DaAe.out.gz", col_names = headers) %>% filter(!grepl("_Random_", query.acc.ver))
Boleracea_vs_DaAe_A <- Boleracea_vs_DaAe %>%
  filter(grepl("BnachrA",query.acc.ver))
DaAe_vs_Boleracea <- read_table("BlastP/DaAe_vs_Boleracea_HDEM.out.gz", col_names = headers) %>% filter(!grepl("_Random_", subject.acc.ver))
DaAe_A_vs_Boleracea <- DaAe_vs_Boleracea %>%
  filter(grepl("BnachrA",subject.acc.ver))

# Filter for best hits
Boleracea_vs_DaAe_A <- Boleracea_vs_DaAe_A %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
DaAe_A_vs_Boleracea <- DaAe_A_vs_Boleracea %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Boleracea_and_DaAe_A <- inner_join(Boleracea_vs_DaAe_A,
                                  DaAe_A_vs_Boleracea,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for DaAe_C and Boleracea
# Find the RBH between DaAe_C and Boleracea
Boleracea_vs_DaAe_C <- Boleracea_vs_DaAe %>%
  filter(grepl("BnachrC",query.acc.ver))
DaAe_C_vs_Boleracea <- DaAe_vs_Boleracea %>%
  filter(grepl("BnachrC",subject.acc.ver))

# Filter for best hits
Boleracea_vs_DaAe_C <- Boleracea_vs_DaAe_C %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
DaAe_C_vs_Boleracea <- DaAe_C_vs_Boleracea %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Boleracea_and_DaAe_C <- inner_join(Boleracea_vs_DaAe_C,
                                  DaAe_C_vs_Boleracea,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for DaAe_A and DaAe_C
# Find the RBH between DaAe_A and DaAe_C
DaAe_A_vs_DaAe_C <- read_table("BlastP/DaAe_A_vs_DaAe_C.out.gz", col_names = headers) %>% filter(!grepl("_Random_", query.acc.ver))
DaAe_C_vs_DaAe_A <- read_table("BlastP/DaAe_C_vs_DaAe_A.out.gz", col_names = headers) %>% filter(!grepl("_Random_", subject.acc.ver))

# Filter for best hits
DaAe_A_vs_DaAe_C <- DaAe_A_vs_DaAe_C %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
DaAe_C_vs_DaAe_A <- DaAe_C_vs_DaAe_A %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
DaAe_A_and_DaAe_C <- inner_join(DaAe_A_vs_DaAe_C,
                                  DaAe_C_vs_DaAe_A,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))
```

For simplicity of the analysis, orthogonal genes between B.rapa and B.oleracea were used to filter potential sites of homeologous exchange between DaAe's two subgenomes, A and C. Homeologous exchange is the exchange of genetic material from one subgenome to the other. In this case it would be the conversion of an A subgenome gene to a C subgenome gene or vice versa. Brassica napus is an allo-tetraploid containing two diploid subgenomes A and C, meaning homeologous exchange can result in homeologous gene ratios of 2:2, 3:1, and 4:0 corresponding to a reciprocal, partial, or complete gene transversion. Because the present assembly is unphased, attempting to identify potential 3:1 homeologous gene ratios is inhibited by the assembler program either selecting one of the two homeologous genes or creating a mashup of the two genes when creating the consensus sequence. In both cases, the true underlying biology is not being accurately represented in the assembly sequence. For this reason, complete gene transversions were the group of focus in this homeologous analysis.

## Find potential sites where a C gene in the C subgenome was converted to an A gene

For a potential homeologous gene pair to be considered as a possible site of homeologous exchange, two requirements must be met. First, the gene must align better to its homeolog than it does to its ortholog. Second, the gene must also align better to its homeolog's ortholog than it does to its ortholog. If an annotation is incomplete or erroneous, it can create both false positive and false negative results.

Compare alignments
If HE both true:
  Rule 1: An-Cn > Co-Cn
  Rule 2: Ar-Cn > Co-Cn
  
```{r}
HE_of_A <- function(ArCo, ArAn, ArCn, CoCn, AnCn, name){
  # Filter
  Filtered_ArAn <- ArAn %>%
    filter(subject.acc.ver %in% ArCo$subject.acc.ver)
  Filtered_AnCn <- AnCn %>%
    filter(subject.acc.ver %in% Filtered_ArAn$query.acc.ver)

  # Smaller data frames
  Small_AnCn <- Filtered_AnCn %>%
    mutate(pct.identity = (pct.identity.x + pct.identity.y)/2,
           alignment.length = (alignment.length.x + alignment.length.y)/2,
           bit.score = (bit.score.x + bit.score.y) / 2,) %>%
    select(query.acc.ver, subject.acc.ver,
           pct.identity,
           alignment.length,
           bit.score)
  Small_CoCn <- CoCn %>%
    mutate(pct.identity = (pct.identity.x + pct.identity.y)/2,
           alignment.length = (alignment.length.x + alignment.length.y)/2,
           bit.score = (bit.score.x + bit.score.y) / 2,) %>%
    select(query.acc.ver, subject.acc.ver,
           pct.identity,
           alignment.length,
           bit.score)
  Small_ArCn <- ArCn %>%
    mutate(pct.identity = (pct.identity.x + pct.identity.y)/2,
           alignment.length = (alignment.length.x + alignment.length.y)/2,
           bit.score = (bit.score.x + bit.score.y) / 2,) %>%
    select(query.acc.ver, subject.acc.ver,
           pct.identity,
           alignment.length,
           bit.score)
  
  # Rule 1 genes An-Cn > Co-Cn
  Passed_Rule_1 <- Small_AnCn %>%
    left_join(Small_CoCn, by = c("query.acc.ver" = "query.acc.ver"), suffix = c(paste0("_", name) ,"_Oleracea")) %>%
    filter(get(paste0("bit.score_", name)) > bit.score_Oleracea)
  
  # Rule 2 genes Ar-Cn > Co-Cn
  Passed_Rule_2 <- Small_ArCn %>%
    left_join(Small_CoCn, by = c("query.acc.ver" = "query.acc.ver"), suffix = c("_Rapa","_Oleracea")) %>%
    filter(bit.score_Rapa > bit.score_Oleracea)
  
  # Combine rules
  Small_Rule_1 <- Passed_Rule_1 %>%
    select(query.acc.ver, subject.acc.ver = paste0("subject.acc.ver_", name))
  Small_Rule_2 <- Passed_Rule_2 %>%
    select(query.acc.ver, subject.acc.ver = subject.acc.ver_Rapa)
  Combined_Rules <- Small_Rule_1 %>%
    filter(query.acc.ver %in% Small_Rule_2$query.acc.ver)
  Possible_Double_A <- Combined_Rules %>%
    left_join(Filtered_AnCn)
  
  return(Possible_Double_A)
}

DaAe_Double_A <- HE_of_A(ArCo = Brapa_and_Boleracea,
                         ArAn = Brapa_and_DaAe_A,
                         ArCn = Brapa_and_DaAe_C,
                         CoCn = Boleracea_and_DaAe_C,
                         AnCn = DaAe_A_and_DaAe_C,
                         name = "DaAe")
```

## Find potential sites where an A gene in the A subgenome was converted to a C gene


Compare alignments
If HE both true:
  Rule 1: An-Cn > Ar-An
  Rule 2: Co-An > Ar-An

```{r}
HE_of_C <- function(ArCo, ArAn, CoAn, CoCn, AnCn, name){
  # Filter
  Filtered_CoCn <- CoCn %>%
    filter(subject.acc.ver %in% ArCo$query.acc.ver)
  Filtered_AnCn <- AnCn %>%
    filter(query.acc.ver %in% Filtered_CoCn$query.acc.ver)

  # Smaller data frames
  Small_AnCn <- Filtered_AnCn %>%
    mutate(pct.identity = (pct.identity.x + pct.identity.y)/2,
           alignment.length = (alignment.length.x + alignment.length.y)/2,
           bit.score = (bit.score.x + bit.score.y) / 2,) %>%
    select(query.acc.ver, subject.acc.ver,
           pct.identity,
           alignment.length,
           bit.score)
  Small_ArAn <- ArAn %>%
    mutate(pct.identity = (pct.identity.x + pct.identity.y)/2,
           alignment.length = (alignment.length.x + alignment.length.y)/2,
           bit.score = (bit.score.x + bit.score.y) / 2,) %>%
    select(query.acc.ver, subject.acc.ver,
           pct.identity,
           alignment.length,
           bit.score)
  Small_CoAn <- CoAn %>%
    mutate(pct.identity = (pct.identity.x + pct.identity.y)/2,
           alignment.length = (alignment.length.x + alignment.length.y)/2,
           bit.score = (bit.score.x + bit.score.y) / 2,) %>%
    select(query.acc.ver, subject.acc.ver,
           pct.identity,
           alignment.length,
           bit.score)
  
  # Rule 1 genes An-Cn > Co-Cn
  Passed_Rule_1 <- Small_AnCn %>%
    left_join(Small_ArAn, by = c("subject.acc.ver" = "query.acc.ver"), suffix = c(paste0("_", name) ,"_Rapa")) %>%
    filter(get(paste0("bit.score_", name)) > bit.score_Rapa)
  
  # Rule 2 genes Ar-Cn > Co-Cn
  Passed_Rule_2 <- Small_CoAn %>%
    left_join(Small_ArAn, by = c("query.acc.ver" = "query.acc.ver"), suffix = c("_Oleracea","_Rapa")) %>%
    filter(bit.score_Oleracea > bit.score_Rapa)
  
  # Combine rules
  Small_Rule_1 <- Passed_Rule_1 %>%
    select(query.acc.ver, subject.acc.ver)
  Small_Rule_2 <- Passed_Rule_2 %>%
    select(query.acc.ver, subject.acc.ver = subject.acc.ver_Oleracea)
  Combined_Rules <- Small_Rule_1 %>%
    filter(subject.acc.ver %in% Small_Rule_2$query.acc.ver)
  Possible_Double_C <- Combined_Rules %>%
    left_join(Filtered_AnCn)
  
  return(Possible_Double_C)
}

DaAe_Double_C <- HE_of_C(ArCo = Brapa_and_Boleracea,
                         ArAn = Brapa_and_DaAe_A,
                         CoAn = Boleracea_and_DaAe_A,
                         CoCn = Boleracea_and_DaAe_C,
                         AnCn = DaAe_A_and_DaAe_C,
                         name = "DaAe")
```


## Looking at coverage of genes in BED files

To look at the coverage of the genes listed in the BED files, the trimmed 10X reads were mapped to a combined progenitor genome containing A01-A10 from B.rapa and C01-C09 from B.oleracea using BWA. To look at possible sites of homeologous exchange, a subsample of reads with unique trustworthy mapping locations was desired. These were reads which could realiably be described as coming from either the A or C subgenome. Alignments were filtered to only contain reads which had a MAPQ of 5 or greater, were properly paired, had no supplementary alignments, and were primary alignments. This subsample of reads was then mapped to the DaAe assembly and filtered for alignments with a MAPQ of 5 or greater. The two alignment files, filtered progenitor and DaAe, were then used to calculate the coverage of their potential homeologous genes using bedtools coverage and the previously created BED files.

```{r}
## Length of gene was also factored into coverage estimates
## For simplicity, the coverage of all genes was calculated then subset for the potential HE genes
## Starting with the coverage of the progenitor genes

## Read in the calculated coverages
Coverage_Readin <- function(filename){
  df <- read_delim(filename,
                   col_names = c("Chromosome","Start","End","GeneId","Score","Strand","Coverage", "Covered", "Size", "Ratio"),
                   delim = "\t") %>%
    mutate(Adjusted_Coverage = round(Coverage / Size, 2),
           Position = floor((End + Start) / 2)) %>%
    group_by(Chromosome) %>%
    mutate(Chromosome_Average = mean(Coverage),
           Chromosome_SD = sd(Coverage),
           Adjusted_Chromosome_Average = mean(Adjusted_Coverage),
           Adjusted_Chromosome_SD = sd(Adjusted_Coverage)) %>%
    ungroup()
  return(df)
}


Pseudo_napus_Coverage <- Coverage_Readin("Coverages/Gene/pseudo_napus_Gene_coverage.tsv")
DaAe_Coverage <- Coverage_Readin("Coverages/Gene/DaAe_Gene_coverage.tsv")
```

# Double A in Progenitor genes

```{r}
DA_Pseudo_napus_Formatter <- function(ArCo,
                                      Pseudo_napus_Coverage,
                                      ArAn,
                                      Double_A,
                                      cutoff = 2.5){
  df <- ArAn %>%
    filter(query.acc.ver %in% Double_A$subject.acc.ver) %>%
    select(subject.acc.ver) %>%
    inner_join(ArCo, by = "subject.acc.ver") %>%
    select(query.acc.ver, subject.acc.ver) %>%
    mutate(subject.acc.ver = str_remove(subject.acc.ver, "Parent=")) %>%
    left_join(Pseudo_napus_Coverage %>%
                select(GeneId, Adjusted_Coverage), by = c("subject.acc.ver" = "GeneId")) %>%
    select(Rapa = subject.acc.ver, Oleracea = query.acc.ver, Rapa_coverage = Adjusted_Coverage) %>%
    left_join(Pseudo_napus_Coverage %>%
                select(GeneId, Adjusted_Coverage), by = c("Oleracea" = "GeneId")) %>%
    select(Rapa, Oleracea, Rapa_coverage, Oleracea_coverage = Adjusted_Coverage) %>%
    filter(Rapa_coverage > 0 & Rapa_coverage > cutoff*Oleracea_coverage) %>%
    mutate(Ratio = round(Rapa_coverage/Oleracea_coverage,2)) %>%
    arrange(Rapa)
  return(df)
}

DA_Pseudo_napus_DaAe <- DA_Pseudo_napus_Formatter(Brapa_and_Boleracea,
                                      Pseudo_napus_Coverage,
                                      Brapa_and_DaAe_A,
                                      DaAe_Double_A,
                                      cutoff = 2.5)

```

# Double C in Progenitor genes

```{r}
DC_Pseudo_napus_Formatter <- function(ArCo,
                                    Pseudo_napus_Coverage,
                                    CoCn,
                                    Double_C,
                                    cutoff = 2.5){
  df <- CoCn %>%
    filter(query.acc.ver %in% Double_C$query.acc.ver) %>%
    select(subject.acc.ver) %>%
    inner_join(ArCo, by = c("subject.acc.ver" = "query.acc.ver")) %>%
    select(qseqid = subject.acc.ver.y, sseqid = subject.acc.ver) %>%
    mutate(qseqid = str_remove(qseqid, "Parent=")) %>%
    left_join(Pseudo_napus_Coverage %>%
                select(GeneId, Adjusted_Coverage), by = c("qseqid" = "GeneId")) %>%
    select(Rapa = qseqid, Oleracea = sseqid, Rapa_coverage = Adjusted_Coverage) %>%
    left_join(Pseudo_napus_Coverage %>%
                select(GeneId, Adjusted_Coverage), by = c("Oleracea" = "GeneId")) %>%
    select(Rapa, Oleracea, Rapa_coverage, Oleracea_coverage = Adjusted_Coverage) %>%
    filter(Oleracea_coverage > 0 & Oleracea_coverage > cutoff*Rapa_coverage) %>%
    mutate(Ratio = round(Oleracea_coverage/Rapa_coverage,2)) %>%
    arrange(Rapa)
  return(df)
}

DC_Pseudo_napus_DaAe <- DC_Pseudo_napus_Formatter(Brapa_and_Boleracea,
                                                  Pseudo_napus_Coverage,
                                                  Boleracea_and_DaAe_C,
                                                  DaAe_Double_C,
                                                  cutoff = 2.5)

```

# Double A and Double C in Napus genes

```{r}
Double_Pseudo_napus_Formatter <- function(Query_Coverage, Double, cutoff_min = 0.5, cutoff_max = 1.5){
  df <- Double %>%
    select(qseqid = query.acc.ver, sseqid = subject.acc.ver) %>%
    left_join(Query_Coverage, by = c("sseqid" = "GeneId")) %>%
    select(Genome_A = sseqid, Genome_C = qseqid, Genome_A_coverage = Adjusted_Coverage) %>%
    left_join(Query_Coverage, by = c("Genome_C" = "GeneId")) %>%
    select(Genome_A, Genome_C, Genome_A_coverage, Genome_C_coverage = Adjusted_Coverage) %>%
    mutate(Ratio = round(Genome_A_coverage / Genome_C_coverage, 2)) %>%
    filter(Genome_A_coverage > 0 & Genome_C_coverage > 0 & Ratio >= cutoff_min & Ratio <= cutoff_max) %>%
    arrange(Genome_A)
  return(df)
}

DA_DaAe <- Double_Pseudo_napus_Formatter(DaAe_Coverage, DaAe_Double_A)
DC_DaAe <- Double_Pseudo_napus_Formatter(DaAe_Coverage, DaAe_Double_C)
```

## Combining the progenitor and napus coverages

```{r}

Coverage_Combiner <- function(ArCo, ArCo_Coverage, Query_Alignment, Query_Alignment_2, Query_Coverage){
  df <- Query_Alignment %>%
    mutate(subject.acc.ver = str_remove(subject.acc.ver, "Parent=")) %>%
    filter(subject.acc.ver %in% ArCo_Coverage$Rapa) %>%
    filter(query.acc.ver %in% Query_Coverage$Genome_A) %>%
    select(Rapa = subject.acc.ver, Genome_A = query.acc.ver) %>%
    left_join(ArCo %>% mutate(subject.acc.ver = str_remove(subject.acc.ver, "Parent=")),
              by = c("Rapa" = "subject.acc.ver")) %>%
    filter(query.acc.ver %in% ArCo_Coverage$Oleracea) %>%
    select(Rapa, Oleracea = query.acc.ver, Genome_A) %>%
    left_join(Query_Alignment_2, by = c("Oleracea" = "subject.acc.ver")) %>%
    filter(query.acc.ver %in% Query_Coverage$Genome_C) %>%
    select(Rapa, Oleracea, Genome_A, Genome_C = "query.acc.ver") %>%
    left_join(Query_Coverage %>%
                select(Genome_A, Ratio)) %>%
    select(Rapa, Oleracea, Genome_A, Genome_C, Napus_Ratio = Ratio) %>%
    left_join(ArCo_Coverage %>%
                select(Rapa, Ratio)) %>%
    select(Rapa, Oleracea, Genome_A, Genome_C, Napus_Ratio, ArCo_Ratio = Ratio) %>%
    arrange(Rapa) %>%
    mutate(ArCo_Ratio = ifelse(is.infinite(ArCo_Ratio),
                                     5,
                                     ifelse(ArCo_Ratio > 5,
                                            5,
                                            ArCo_Ratio)),
           Group = 1:nrow(.))
  return(df)
}

DA_Combined_DaAe <- Coverage_Combiner(Brapa_and_Boleracea, DA_Pseudo_napus_DaAe, Brapa_and_DaAe_A, Boleracea_and_DaAe_C, DA_DaAe)
DC_Combined_DaAe <- Coverage_Combiner(Brapa_and_Boleracea, DC_Pseudo_napus_DaAe, Brapa_and_DaAe_A, Boleracea_and_DaAe_C, DC_DaAe)

```

```{r}
save(DA_Combined_DaAe, DC_Combined_DaAe, file = "DaAe_gene_doublings.RData")
```

### Extracting positions of genes

```{r}

Position_Extract <- function(Combined_Coverage, Pseudo_napus_Coverage, Napus_Coverage){
  GeneId <- c(Combined_Coverage$Rapa,Combined_Coverage$Oleracea,Combined_Coverage$Genome_A,Combined_Coverage$Genome_C)
  Group = rep(Combined_Coverage$Group,4)
  Assembly = rep(c("Pseudo_napus", "Napus"), each = length(GeneId)/2)
  df <- data.frame(GeneId, Group, Assembly, stringsAsFactors = F)
  df <- df %>%
    left_join(rbind(Pseudo_napus_Coverage, Napus_Coverage) %>%
                select(GeneId, Chromosome, Position))
  return(df)
}

DA_DaAe_Positions <- Position_Extract(DA_Combined_DaAe, Pseudo_napus_Coverage, DaAe_Coverage)
DC_DaAe_Positions <- Position_Extract(DC_Combined_DaAe, Pseudo_napus_Coverage, DaAe_Coverage)

save(DA_DaAe_Positions, DC_DaAe_Positions, file = "DaAe_Gene_Positions.RData")
```

## ZS11
```{r}
# Repeat for DaAe_A and Brapa
# Find the RBH between DaAe_A and Brapa
Brapa_vs_ZS11 <- read_table("BlastP/Brapa_Z1_V2_vs_ZS11.out.gz", col_names = headers) %>% filter(!grepl("Bnascaffold", query.acc.ver))
Brapa_vs_ZS11_A <- Brapa_vs_ZS11 %>%
  filter(grepl("BnaA",query.acc.ver))
ZS11_vs_Brapa <- read_table("BlastP/ZS11_vs_Brapa_Z1_V2.out.gz", col_names = headers) %>% filter(!grepl("Bnascaffold", subject.acc.ver))
ZS11_A_vs_Brapa <- ZS11_vs_Brapa %>%
  filter(grepl("BnaA",subject.acc.ver))

# Filter for best hits
Brapa_vs_ZS11_A <- Brapa_vs_ZS11_A %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
ZS11_A_vs_Brapa <- ZS11_A_vs_Brapa %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Brapa_and_ZS11_A <- inner_join(Brapa_vs_ZS11_A,
                                  ZS11_A_vs_Brapa,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for ZS11_C and Brapa
# Find the RBH between ZS11_C and Brapa
Brapa_vs_ZS11_C <- Brapa_vs_ZS11 %>%
  filter(grepl("BnaC",query.acc.ver))
ZS11_C_vs_Brapa <- ZS11_vs_Brapa %>%
  filter(grepl("BnaC",subject.acc.ver))

# Filter for best hits
Brapa_vs_ZS11_C <- Brapa_vs_ZS11_C %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
ZS11_C_vs_Brapa <- ZS11_C_vs_Brapa %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Brapa_and_ZS11_C <- inner_join(Brapa_vs_ZS11_C,
                                  ZS11_C_vs_Brapa,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for ZS11_A and Boleracea
# Find the RBH between ZS11_A and Boleracea
Boleracea_vs_ZS11 <- read_table("BlastP/Boleracea_HDEM_vs_ZS11.out.gz", col_names = headers) %>% filter(!grepl("Bnascaffold", query.acc.ver))
Boleracea_vs_ZS11_A <- Boleracea_vs_ZS11 %>%
  filter(grepl("BnaA",query.acc.ver))
ZS11_vs_Boleracea <- read_table("BlastP/ZS11_vs_Boleracea_HDEM.out.gz", col_names = headers) %>% filter(!grepl("Bnascaffold", subject.acc.ver))
ZS11_A_vs_Boleracea <- ZS11_vs_Boleracea %>%
  filter(grepl("BnaA",subject.acc.ver))

# Filter for best hits
Boleracea_vs_ZS11_A <- Boleracea_vs_ZS11_A %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
ZS11_A_vs_Boleracea <- ZS11_A_vs_Boleracea %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Boleracea_and_ZS11_A <- inner_join(Boleracea_vs_ZS11_A,
                                  ZS11_A_vs_Boleracea,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for ZS11_C and Boleracea
# Find the RBH between ZS11_C and Boleracea
Boleracea_vs_ZS11_C <- Boleracea_vs_ZS11 %>%
  filter(grepl("BnaC",query.acc.ver))
ZS11_C_vs_Boleracea <- ZS11_vs_Boleracea %>%
  filter(grepl("BnaC",subject.acc.ver))

# Filter for best hits
Boleracea_vs_ZS11_C <- Boleracea_vs_ZS11_C %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
ZS11_C_vs_Boleracea <- ZS11_C_vs_Boleracea %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Boleracea_and_ZS11_C <- inner_join(Boleracea_vs_ZS11_C,
                                  ZS11_C_vs_Boleracea,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for ZS11_A and ZS11_C
# Find the RBH between ZS11_A and ZS11_C
ZS11_A_vs_ZS11_C <- read_table("BlastP/ZS11_A_vs_ZS11_C.out.gz", col_names = headers) %>% filter(!grepl("Bnascaffold", query.acc.ver))
ZS11_C_vs_ZS11_A <- read_table("BlastP/ZS11_C_vs_ZS11_A.out.gz", col_names = headers) %>% filter(!grepl("Bnascaffold", subject.acc.ver))

# Filter for best hits
ZS11_A_vs_ZS11_C <- ZS11_A_vs_ZS11_C %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
ZS11_C_vs_ZS11_A <- ZS11_C_vs_ZS11_A %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
ZS11_A_and_ZS11_C <- inner_join(ZS11_A_vs_ZS11_C,
                                  ZS11_C_vs_ZS11_A,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

ZS11_Double_A <- HE_of_A(ArCo = Brapa_and_Boleracea,
                         ArAn = Brapa_and_ZS11_A,
                         ArCn = Brapa_and_ZS11_C,
                         CoCn = Boleracea_and_ZS11_C,
                         AnCn = ZS11_A_and_ZS11_C,
                         name = "ZS11")


ZS11_Double_C <- HE_of_C(ArCo = Brapa_and_Boleracea,
                         ArAn = Brapa_and_ZS11_A,
                         CoAn = Boleracea_and_ZS11_A,
                         CoCn = Boleracea_and_ZS11_C,
                         AnCn = ZS11_A_and_ZS11_C,
                         name = "ZS11")

Pseudo_napus_Coverage <- Coverage_Readin("Coverages/Gene/pseudo_napus_Gene_coverage.tsv")
ZS11_Coverage <- Coverage_Readin("Coverages/Gene/ZS11_Gene_coverage.tsv")

DA_Pseudo_napus_ZS11 <- DA_Pseudo_napus_Formatter(Brapa_and_Boleracea,
                                      Pseudo_napus_Coverage,
                                      Brapa_and_ZS11_A,
                                      ZS11_Double_A,
                                      cutoff = 2.5)


DC_Pseudo_napus_ZS11 <- DC_Pseudo_napus_Formatter(Brapa_and_Boleracea,
                                                  Pseudo_napus_Coverage,
                                                  Boleracea_and_ZS11_C,
                                                  ZS11_Double_C,
                                                  cutoff = 2.5)


DA_ZS11 <- Double_Pseudo_napus_Formatter(ZS11_Coverage, ZS11_Double_A)
DC_ZS11 <- Double_Pseudo_napus_Formatter(ZS11_Coverage, ZS11_Double_C)

DA_Combined_ZS11 <- Coverage_Combiner(Brapa_and_Boleracea, DA_Pseudo_napus_ZS11, Brapa_and_ZS11_A, Boleracea_and_ZS11_C, DA_ZS11)
DC_Combined_ZS11 <- Coverage_Combiner(Brapa_and_Boleracea, DC_Pseudo_napus_ZS11, Brapa_and_ZS11_A, Boleracea_and_ZS11_C, DC_ZS11)

save(DA_Combined_ZS11, DC_Combined_ZS11, file = "ZS11_gene_doublings.RData")

DA_ZS11_Positions <- Position_Extract(DA_Combined_ZS11, Pseudo_napus_Coverage, ZS11_Coverage)
DC_ZS11_Positions <- Position_Extract(DC_Combined_ZS11, Pseudo_napus_Coverage, ZS11_Coverage)

save(DA_ZS11_Positions, DC_ZS11_Positions, file = "ZS11_Gene_Positions.RData")
```

## Darmor_Bzh_V10
```{r}
# Repeat for DaAe_A and Brapa
# Find the RBH between DaAe_A and Brapa
Brapa_vs_Darmor_Bzh_V10 <- read_table("BlastP/Brapa_Z1_V2_vs_Darmor_Bzh_V10.out.gz", col_names = headers) %>% filter(!grepl("scaffold", query.acc.ver))
Brapa_vs_Darmor_Bzh_V10_A <- Brapa_vs_Darmor_Bzh_V10 %>%
  filter(grepl("^A",query.acc.ver))
Darmor_Bzh_V10_vs_Brapa <- read_table("BlastP/Darmor_Bzh_V10_vs_Brapa_Z1_V2.out.gz", col_names = headers) %>% filter(!grepl("scaffold", subject.acc.ver))
Darmor_Bzh_V10_A_vs_Brapa <- Darmor_Bzh_V10_vs_Brapa %>%
  filter(grepl("^A",subject.acc.ver))

# Filter for best hits
Brapa_vs_Darmor_Bzh_V10_A <- Brapa_vs_Darmor_Bzh_V10_A %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
Darmor_Bzh_V10_A_vs_Brapa <- Darmor_Bzh_V10_A_vs_Brapa %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Brapa_and_Darmor_Bzh_V10_A <- inner_join(Brapa_vs_Darmor_Bzh_V10_A,
                                  Darmor_Bzh_V10_A_vs_Brapa,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for Darmor_Bzh_V10_C and Brapa
# Find the RBH between Darmor_Bzh_V10_C and Brapa
Brapa_vs_Darmor_Bzh_V10_C <- Brapa_vs_Darmor_Bzh_V10 %>%
  filter(grepl("^C",query.acc.ver))
Darmor_Bzh_V10_C_vs_Brapa <- Darmor_Bzh_V10_vs_Brapa %>%
  filter(grepl("^C",subject.acc.ver))

# Filter for best hits
Brapa_vs_Darmor_Bzh_V10_C <- Brapa_vs_Darmor_Bzh_V10_C %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
Darmor_Bzh_V10_C_vs_Brapa <- Darmor_Bzh_V10_C_vs_Brapa %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Brapa_and_Darmor_Bzh_V10_C <- inner_join(Brapa_vs_Darmor_Bzh_V10_C,
                                  Darmor_Bzh_V10_C_vs_Brapa,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for Darmor_Bzh_V10_A and Boleracea
# Find the RBH between Darmor_Bzh_V10_A and Boleracea
Boleracea_vs_Darmor_Bzh_V10 <- read_table("BlastP/Boleracea_HDEM_vs_Darmor-Bzh_V10.out.gz", col_names = headers) %>% filter(!grepl("scaffold", query.acc.ver))
Boleracea_vs_Darmor_Bzh_V10_A <- Boleracea_vs_Darmor_Bzh_V10 %>%
  filter(grepl("^A",query.acc.ver))
Darmor_Bzh_V10_vs_Boleracea <- read_table("BlastP/Darmor-Bzh_V10_vs_Boleracea_HDEM.out.gz", col_names = headers) %>% filter(!grepl("scaffold", subject.acc.ver))
Darmor_Bzh_V10_A_vs_Boleracea <- Darmor_Bzh_V10_vs_Boleracea %>%
  filter(grepl("^A",subject.acc.ver))

# Filter for best hits
Boleracea_vs_Darmor_Bzh_V10_A <- Boleracea_vs_Darmor_Bzh_V10_A %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
Darmor_Bzh_V10_A_vs_Boleracea <- Darmor_Bzh_V10_A_vs_Boleracea %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Boleracea_and_Darmor_Bzh_V10_A <- inner_join(Boleracea_vs_Darmor_Bzh_V10_A,
                                  Darmor_Bzh_V10_A_vs_Boleracea,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for Darmor_Bzh_V10_C and Boleracea
# Find the RBH between Darmor_Bzh_V10_C and Boleracea
Boleracea_vs_Darmor_Bzh_V10_C <- Boleracea_vs_Darmor_Bzh_V10 %>%
  filter(grepl("^C",query.acc.ver))
Darmor_Bzh_V10_C_vs_Boleracea <- Darmor_Bzh_V10_vs_Boleracea %>%
  filter(grepl("^C",subject.acc.ver))

# Filter for best hits
Boleracea_vs_Darmor_Bzh_V10_C <- Boleracea_vs_Darmor_Bzh_V10_C %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
Darmor_Bzh_V10_C_vs_Boleracea <- Darmor_Bzh_V10_C_vs_Boleracea %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Boleracea_and_Darmor_Bzh_V10_C <- inner_join(Boleracea_vs_Darmor_Bzh_V10_C,
                                  Darmor_Bzh_V10_C_vs_Boleracea,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))

# Repeat for Darmor_Bzh_V10_A and Darmor_Bzh_V10_C
# Find the RBH between Darmor_Bzh_V10_A and Darmor_Bzh_V10_C
Darmor_Bzh_V10_A_vs_Darmor_Bzh_V10_C <- read_table("BlastP/Darmor-Bzh_V10_A_vs_Darmor-Bzh_V10_C.out.gz", col_names = headers) %>% filter(!grepl("scaffold", query.acc.ver))
Darmor_Bzh_V10_C_vs_Darmor_Bzh_V10_A <- read_table("BlastP/Darmor-Bzh_V10_C_vs_Darmor-Bzh_V10_A.out.gz", col_names = headers) %>% filter(!grepl("scaffold", subject.acc.ver))

# Filter for best hits
Darmor_Bzh_V10_A_vs_Darmor_Bzh_V10_C <- Darmor_Bzh_V10_A_vs_Darmor_Bzh_V10_C %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()
Darmor_Bzh_V10_C_vs_Darmor_Bzh_V10_A <- Darmor_Bzh_V10_C_vs_Darmor_Bzh_V10_A %>%
  group_by(query.acc.ver) %>%
  slice_max(order_by = bit.score, n = 1, with_ties = FALSE) %>%
  ungroup()

# Merge together
Darmor_Bzh_V10_A_and_Darmor_Bzh_V10_C <- inner_join(Darmor_Bzh_V10_A_vs_Darmor_Bzh_V10_C,
                                  Darmor_Bzh_V10_C_vs_Darmor_Bzh_V10_A,
                                  by = c("query.acc.ver" = "subject.acc.ver",
                                         "subject.acc.ver" = "query.acc.ver"))


Darmor_Bzh_V10_Double_A <- HE_of_A(ArCo = Brapa_and_Boleracea,
                         ArAn = Brapa_and_Darmor_Bzh_V10_A,
                         ArCn = Brapa_and_Darmor_Bzh_V10_C,
                         CoCn = Boleracea_and_Darmor_Bzh_V10_C,
                         AnCn = Darmor_Bzh_V10_A_and_Darmor_Bzh_V10_C,
                         name = "Darmor_Bzh_V10")


Darmor_Bzh_V10_Double_C <- HE_of_C(ArCo = Brapa_and_Boleracea,
                         ArAn = Brapa_and_Darmor_Bzh_V10_A,
                         CoAn = Boleracea_and_Darmor_Bzh_V10_A,
                         CoCn = Boleracea_and_Darmor_Bzh_V10_C,
                         AnCn = Darmor_Bzh_V10_A_and_Darmor_Bzh_V10_C,
                         name = "Darmor_Bzh_V10")


Pseudo_napus_Coverage <- Coverage_Readin("Coverages/Gene/pseudo_napus_Gene_coverage.tsv")
Darmor_Bzh_V10_Coverage <- Coverage_Readin("Coverages/Gene/Darmor-Bzh_V10_Gene_coverage.tsv")


DA_Pseudo_napus_Darmor_Bzh_V10 <- DA_Pseudo_napus_Formatter(Brapa_and_Boleracea,
                                      Pseudo_napus_Coverage,
                                      Brapa_and_Darmor_Bzh_V10_A,
                                      Darmor_Bzh_V10_Double_A,
                                      cutoff = 2.5)


DC_Pseudo_napus_Darmor_Bzh_V10 <- DC_Pseudo_napus_Formatter(Brapa_and_Boleracea,
                                                  Pseudo_napus_Coverage,
                                                  Boleracea_and_Darmor_Bzh_V10_C,
                                                  Darmor_Bzh_V10_Double_C,
                                                  cutoff = 2.5)


DA_Darmor_Bzh_V10 <- Double_Pseudo_napus_Formatter(Darmor_Bzh_V10_Coverage, Darmor_Bzh_V10_Double_A)
DC_Darmor_Bzh_V10 <- Double_Pseudo_napus_Formatter(Darmor_Bzh_V10_Coverage, Darmor_Bzh_V10_Double_C)

DA_Combined_Darmor_Bzh_V10 <- Coverage_Combiner(Brapa_and_Boleracea, DA_Pseudo_napus_Darmor_Bzh_V10, Brapa_and_Darmor_Bzh_V10_A, Boleracea_and_Darmor_Bzh_V10_C, DA_Darmor_Bzh_V10)
DC_Combined_Darmor_Bzh_V10 <- Coverage_Combiner(Brapa_and_Boleracea, DC_Pseudo_napus_Darmor_Bzh_V10, Brapa_and_Darmor_Bzh_V10_A, Boleracea_and_Darmor_Bzh_V10_C, DC_Darmor_Bzh_V10)

save(DA_Combined_Darmor_Bzh_V10, DC_Combined_Darmor_Bzh_V10, file = "Darmor-Bzh_V10_gene_doublings.RData")

DA_Darmor_Bzh_V10_Positions <- Position_Extract(DA_Combined_Darmor_Bzh_V10, Pseudo_napus_Coverage, Darmor_Bzh_V10_Coverage)
DC_Darmor_Bzh_V10_Positions <- Position_Extract(DC_Combined_Darmor_Bzh_V10, Pseudo_napus_Coverage, Darmor_Bzh_V10_Coverage)

save(DA_Darmor_Bzh_V10_Positions, DC_Darmor_Bzh_V10_Positions, file = "Darmor-Bzh_V10_Gene_Positions.RData")
```